You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-26 paper/paper.tex
more progres...

\section{Related Work}
\begin{itemize}
  \item Kevin Knight's work on poetry generation
  \item Any work on writing style (e.g. classification)?  Possibly cite work on author attribution...
  \item work on paraphrase evaluation metrics (David Chen, CCB, etc...)
\end{itemize}

>>>>

Finally we note that overall the average automatc metrics seem to agree with agree with human judgements as displayed in figure \ref{style_metrics}.

\begin{figure}
  \begin{center}
    \includegraphics[width=4in]{figures/style_metrics.pdf}
    \end{center}
    \caption{Overall results from comparing automatic style metrics.  Note that the automatic metrics agree with results from human judgements in figure \ref{human_judgements}.}
    \label{style_metrics}
\end{figure}

\section{Related Work}
Although no previous work has investigated paraphrasing modern text into Shakesperean English, or the more general task of paraphrasing while targeting a specific writing
style, there are several strands of related work.

Perhaps most relevant is recent work generating and translating rhythmic poetry \cite{Greene10}.  This work focused on generating text in an appropriate
meter (e.g. iambic pentameter) using finate-state transducers.  In contrast our work does not address the issue of meter, however it should be possible to combine our translation
models with their weighted FSTs to produce Shakesperean paraphrase models which produce output in an appropriate meter.

Much previous work has addressed the task of automatically generating paraphrases \cite{Callison-Burch08,Kok10}.  In addition several authors have previously proposed 
automatic paraphrase evaluation metrics \cite{Callison-Burch08b,Bangalore00,liu10}.
We are not aware, however, of any previous work that has addressed the task of generating or evaluating
paraphrases targeting a specific style of writing.

Finally we highlight related work on authorship classification which can be seen as detecting a specific style of writing \cite{Gamon04,Raghavan10}.
This work has not specifically addressed the task of automatically generating or evaluating paraphrases in a specific style, however.
